Hypertension and microbiome

### 2019-02-05 articletwo.Rmd
Minor

```{r Running at}
now <- ifelse(exists('now'),now, format(Sys.time(), '%Y%m%d-%H%M%S'))
```

>>>>

```{r Command line arguments}
now <- format(Sys.time(), '%Y%m%d-%H%M%S')

if (exists(args)) {
    if ("time" %in% names(args) now <- args$time,

    if("clean" %in% names(args)) {
        unlink("rds", recursive=TRUE)
        unlink("cache", recursive=TRUE)
    }
}
```
